Pyro-Velocity

### 2024-07-15 nbs/tutorials/introduction.qmd
docs(tutorials): update introduction
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

### Quick start

@@

Please see the [documentation](https://pyrovelocity.readthedocs.io/en/latest/installation.html).

@@

Also see [contributing](./docs/contributing.md).

>>>>

For end-user oriented (i.e. not for development but rather execution)
installation please see the [installation guide](../guides/installation.qmd).
For development installation please see the [contributing guide](../about/contributing.qmd).

<!-- ### Quick start

@@

Please see the [documentation](https://pyrovelocity.readthedocs.io/en/latest/installation.html). -->

@@

Also see [contributing](../about/contributing.qmd).
